A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-01 main.tex
Transition in typing rules in \LTP.

\newcommand{\LTP}{$\lambda^{\triangleright\%}$\xspace}
\newcommand{\LMD}{$\lambda^{\textrm{MD}}$\xspace}
\newcommand{\LLF}{$\lambda^{\textrm{LF}}$\xspace}

@@

@@

Next, we develop \LMD by extending \LTP with dependent types.

@@

\begin{figure}
	\begin{center}
		\infrule{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau@A}{\TConst} \andalso
		\infrule{x:\tau@A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau@A}{\TVar} \\[2mm]
		\infrule{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau@A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A}{\textsc{T-Abs}} \\[2mm]
		\infrule{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A}{\textsc{T-App}} \andalso
		\infrule{\G\V M:\tau@A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A}{\textsc{T-Conv}} \\[2mm]
		\infrule{\G\V M:\tau@{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A}{\textsc{T-$\TB$}} \andalso
		\infrule{\G\V M:\TW_{\alpha}\tau@A}{\G\V\TBL_{\alpha}M:\tau@{A\alpha}}{\TTBL} \\[2mm]
		\infrule{\G\V M:\tau@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau@A}{\textsc{T-Gen}} \andalso
		\infrule{\G\V M:\forall\alpha.\tau@A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A}{\textsc{T-Ins}} \andalso
		\infrule{\G\V M:\tau@A}{\G\V \%_\alpha M:\tau@{A\alpha}}{\textsc{T-Csp}} \andalso
		\caption{Typing Rules}
		\label{fig:typing-rules}
	\end{center}
\end{figure}

>>>>

\newcommand{\LTP}{$\lambda^{\triangleright\%}$\xspace}
\newcommand{\LMD}{$\lambda^{\textrm{MD}}$\xspace}
\newcommand{\LLF}{$\lambda\textrm{LF}$\xspace}

@@

% transition in typing rules

\blue{Should we use $\vdash^A$? or $\vdash @ A$?}

A type judgement of \LTP is of the form $\G \vdash M : \tau @ A$.
Transition $A$ means in which transition $M$ exists.
Therefore, transitions appear in typing rules, too.
\begin{center}
	\infrule{\G\vdash M:\tau@{A\alpha}}{\G\vdash \TB_{\alpha}M:\TW_{\alpha}\tau@A}{\TTB} \andalso
	\infrule{\G\vdash M:\TW_{\alpha}\tau@A}{\G\vdash \TBL_{\alpha}M:\tau@{A\alpha}}{\TTBL}
\end{center}
\TTB, corresponding to quoting, means 
if $M$ is typed $\tau$ at transition $A\alpha$ then $\TB_{\alpha}M$, quoted $M$, is typed $\TW_{\alpha}\tau$ at $A$.
\TTBL is converse of \TTB.

@@

Next, we develop \LMD by extending \LTP with \LLF-like dependent types.

@@

\begin{figure}
	\begin{center}
		\infrule{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau@A}{\TConst} \andalso
		\infrule{x:\tau@A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau@A}{\TVar} \\[2mm]
		\infrule{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau@A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A}{\textsc{T-Abs}} \\[2mm]
		\infrule{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A}{\textsc{T-App}} \andalso
		\infrule{\G\V M:\tau@A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A}{\textsc{T-Conv}} \\[2mm]
		\infrule{\G\V M:\tau@{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau@A}{\TTB} \andalso
		\infrule{\G\V M:\TW_{\alpha}\tau@A}{\G\V\TBL_{\alpha}M:\tau@{A\alpha}}{\TTBL} \\[2mm]
		\infrule{\G\V M:\tau@A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau@A}{\textsc{T-Gen}} \andalso
		\infrule{\G\V M:\forall\alpha.\tau@A}{\G\V M\ \epsilon:\tau[\alpha \mapsto \epsilon]@A}{\textsc{T-Ins}} \andalso
		\infrule{\G\V M:\tau@A}{\G\V \%_\alpha M:\tau@{A\alpha}}{\textsc{T-Csp}} \andalso
		\caption{Typing Rules}
		\label{fig:typing-rules}
	\end{center}
\end{figure}
